\documentclass{article}
\usepackage{preamble}
\input{preamble}
\graphicspath{ {images/} }
%%%%%%%%%%%%%%%% Document %%%%%%%%%%%%%%%%
\begin{document}
\begin{center}
{\huge \underline{H}}
\end{center}

\section{Question 1 (Linear Diffusion)}
Let $u(x,t)$ be a real-valued function. Consider the 1D, unbounded domain, linear diffusion, defined by
\begin{equation}
u_t = u_{xx}, \quad u(x,0) = f(x), \quad t \in [0, \infty)
\end{equation}
where \(t\) is the time variable, \(x\) is the spatial variable, \(u_t\) and \(u_{xx}\) are respectively the time derivative and the second spatial derivative of \(u\), and the function \(f(x)\) is the initial condition.

(a) For a real-valued function \(u \in \mathbb{R}\), show that the solution of the above PDE is a Gaussian convolution with the initial condition, namely
\begin{equation}
u(x,t) = f(x) * g_\sigma(t)(x)
\end{equation}
where \(g_\sigma(t)\) is the Gaussian kernel.

\textbf{\ul{Solution}:} 



Then, find the relation between the time variable \(t\) and the standard deviation \(\sigma\).

(b) Assume the initial condition \(f(x)\) is

\begin{equation}
f(x) = \sin(\omega_1 x) + \sin(\omega_2 x)
\end{equation}

where \(\omega_1, \omega_2\) are positive constants. Use $u(x,t) = f(x) * g_\sigma(t)(x)
 $ to show that \(u(t, x)\) is 

\begin{equation}
u(x,t) = \sin(\omega_1 x)e^{-\omega_1^2 t} + \sin(\omega_2 x)e^{-\omega_2^2 t}.
\end{equation}

(c) For the solution:
\[
  u(x,t) = \sin(\omega_1 x)e^{-\omega_1^2 t} + \sin(\omega_2 x)e^{-\omega_2^2 t}.
\]

1. Write the explicit backward-difference in time expression of \(u(x, \Delta t)\). Keep the spatial coordinates continuous.

2. Write the analytic solution of the approximation of \(u(x, \Delta t)\) given above in (i).

3. Show that the extremum principle is kept under some condition. What is the condition? Is it similar to a stability condition learned in class? Explain.

\end{document}

